\documentclass{resume}
\usepackage[left=0.3in,top=0.25in,right=0.3in,bottom=0.25in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{enumitem}

\setlist[itemize]{noitemsep, topsep=2pt, parsep=0pt, partopsep=0pt, leftmargin=1.2em}
\renewcommand{\labelitemi}{\small$\bullet$}

\definecolor{accent}{HTML}{2B579A}
\definecolor{techgray}{HTML}{3D3D3D}

\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    filecolor=accent,
    urlcolor=accent,
}

% Reusable commands for uniform formatting
\newcommand{\employer}[3]{%
  \vspace{6pt}%
  \textbf{#1} \hfill #2 \enspace$\mid$\enspace #3%
}
\newcommand{\project}[2]{%
  \vspace{6pt}%
  \textbf{#1}\\[1pt]%
  {\footnotesize\textcolor{techgray}{#2}}%
}
\newcommand{\divider}{%
  \vspace{6pt}%
  \noindent\textcolor{techgray}{\rule{\linewidth}{0.3pt}}%
  \vspace{2pt}%
}

\name{Ramacharan Reddy Kasireddy}
\address{
    {\small
    \faEnvelope\ \href{mailto:kramacharanreddy@gmail.com}{kramacharanreddy@gmail.com}
    \enspace$\cdot$\enspace
    \faPhone\ +1 716-292-6481
    \enspace$\cdot$\enspace
    \faLinkedin\ \href{https://www.linkedin.com/in/ramacharanreddy-k/}{ramacharanreddy-k}
    \enspace$\cdot$\enspace
    \faGithub\ \href{https://github.com/ramacharanreddy-k}{ramacharanreddy-k}
    }
}

\begin{document}

\vspace{0.3em}
AI Engineer with 2+ years of experience designing and delivering production AI systems -- multi-agent LangGraph workflows, RAG pipelines with hallucination reduction, vector search, and data ingestion engines -- across both AWS and Azure, with end-to-end ownership from Terraform infrastructure to client-facing delivery.

%==============================================================================
% SKILLS
%==============================================================================
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{3ex}} p{15.2cm} }
AI/ML \& LLMs & LangChain, LangGraph, MCP, RAG (hybrid k-NN + BM25), Prompt Engineering, Fine-Tuning, Multi-Agent Systems, ReAct, Tool Calling, Structured Outputs, Guardrails, Langfuse, LangSmith, Semantic Search, Conversational AI \\[2pt]
LLM Platforms & Azure AI Foundry, Azure OpenAI (GPT-4, Embeddings), AWS Bedrock (Claude, Titan Embeddings), Google Gemini \\[2pt]
Deep Learning & PyTorch, TensorFlow, Hugging Face Transformers, LoRA, PEFT, QLoRA, Quantization, Distillation \\[2pt]
Programming & Python, SQL, JavaScript, Java, React, FastAPI, Uvicorn, Pydantic, Jinja, Playwright, pytest \\[2pt]
Data \& APIs & PostgreSQL, Cosmos DB, OpenSearch, SQLAlchemy, RESTful APIs, OpenAPI/Swagger, OAuth 2.0, JWT, MSAL, JWKS, SSE, WebSockets \\[2pt]
AWS & Bedrock, Bedrock Guardrails, OpenSearch, EKS, ECR, Lambda, SQS, S3, Transcribe, DynamoDB, CodePipeline, KMS, IAM (IRSA) \\[2pt]
Azure & OpenAI Service, Cosmos DB, AKS, ACR, Key Vault, Blob Storage, Entra ID, Managed Identity, Monitor, Logic Apps \\[2pt]
DevOps \& Tools & Docker, Kubernetes, Helm, Terraform, Airflow, Git, GitHub Actions, Jenkins, GitLab CI/CD, GitHub Copilot, Cursor, Claude Code \\
\end{tabular}

\end{rSection}

%==============================================================================
% WORK EXPERIENCE
%==============================================================================
\begin{rSection}{Work Experience}

\employer{Feuji INC}{AI Engineer}{Aug 2024 -- Present}

\project{Customer Analytics AI -- PLZ Corp}{Python, FastAPI, LangGraph, Azure OpenAI, Azure AI Foundry, LangSmith, Cosmos DB, PostgreSQL, Terraform, React}
\\[2pt]
{\small\textit{PLZ needed to track customer growth, monitor industry news, and identify the best time to close deals. The client requested a static reporting dashboard -- I proposed and delivered a conversational AI platform that lets the sales team query all of that data in natural language, replacing weeks of manual research with real-time insights.}}
\begin{itemize}
  \item \textbf{Architected a full-stack AI analytics platform} across 4 microservices (data engine, SSO gateway, conversational agent, React SPA) deployed on AKS, eliminating 48 hours/week of manual analysis and saving \$150K/year.
  \item \textbf{Engineered an AI agent with LangGraph and Azure OpenAI} -- 20 specialized tools, 7-layer middleware stack, and dual-domain RAG over Cosmos DB vector search (DiskANN, 1536-dim embeddings).
  \item \textbf{Grounded all responses in verified data} to reduce hallucinations; added summarization and short-term memory for conversational coherence.
  \item \textbf{Built a multi-stage async data pipeline} (parse, clean, chunk, embed, index, validate, store, sync) ingesting structured and unstructured data into a 12-table PostgreSQL warehouse and a Cosmos DB vector store.
  \item \textbf{Designed a centralized SSO gateway} with FastAPI, MSAL, OAuth2 authorization code flow, Entra ID group-based access control, JWKS S2S validation, and zero hardcoded secrets via Key Vault and Managed Identity.
  \item \textbf{Implemented observability and cost monitoring} -- LangSmith for agent trace debugging and prompt regression testing; Azure Monitor for token-level cost tracking and content safety logging.
  \item \textbf{Provisioned the full Azure environment with Terraform} across 7 modules with passwordless RBAC, covering compute, data, AI, identity, storage, scheduling, and communication services.
  \item \textbf{Recognized by PLZ Corp's Director and CIO} for exceeding project expectations and delivering a platform that transformed their sales decision-making process.
\end{itemize}

\project{Ask the Prospect (ATP) -- TriNet}{Python, FastAPI, LangGraph, AWS Bedrock, Bedrock Guardrails, OpenSearch, Aurora, Langfuse, Airflow, EKS}
\\[2pt]
{\small\textit{TriNet's sales reps typically take 2 years to reach full proficiency. The client asked for a searchable training knowledge base -- I expanded the scope to a multi-mode AI agent combining RAG Q\&A, persona-based role-play coaching, sales analytics, and gamified learning to compress that ramp-up across the entire sales organization.}}
\begin{itemize}
  \item \textbf{Built a multi-mode LangGraph agent} powering 4 capabilities -- RAG chatbot (dual-index: training docs + Gong transcripts), persona-based sales role-play with AI coaching, analytics chat, and automated Jeopardy question generation.
  \item \textbf{Enabled memory continuity} via LangGraph PG checkpointer and store for short-term and long-term memory across sessions.
  \item \textbf{Engineered a sales analytics pipeline} -- LLM enriches each Gong transcript with derived columns (win/loss, objections, competition mentions), then generates OpenSearch queries from natural language for aggregate analysis.
  \item \textbf{Enforced PII protection with AWS Bedrock Guardrails} -- configurable filters that detect and redact sensitive data (names, emails, SSNs) in both inputs and outputs before reaching the client.
  \item \textbf{Integrated Langfuse for observability and cost monitoring} -- LLM-as-judge evaluations for quality scoring, trace-level debugging, latency monitoring, and per-call cost tracking in production.
  \item \textbf{Served as solution architect and client-facing lead}, owning end-to-end technical vision across 4 microservices and 2 Airflow-orchestrated data pipelines on EKS.
  \item \textbf{Recognized by TriNet's CTO, Executive Director, and VP} for expanding scope beyond original requirements and delivering measurable impact to the sales organization.
\end{itemize}

\project{ReQon -- Automated Testing Tool}{Python, LangChain, LangGraph, Google Gemini, Playwright MCP, Aurora PostgreSQL, S3, Docker, pytest}
\\[2pt]
{\small\textit{Feuji is a QA-heavy company where test engineers were spending the bulk of their time writing and maintaining low-level test cases. I led an internal initiative to build an AI platform that auto-discovers application structure and generates test cases and regression scripts from a single browser recording, freeing engineers to focus on high-value exploratory testing.}}
\begin{itemize}
  \item \textbf{Engineered a LangGraph agent with Playwright MCP} that replays a recorded browser flow, navigates every page, and extracts locators, functional elements, and behavioral data into S3 and Aurora PostgreSQL.
  \item \textbf{Automated the full QA authoring workflow} -- from captured browser behavior the agent generates test cases, executes them via Playwright MCP, and outputs verified pass/fail results, eliminating manual test writing.
  \item \textbf{Built a code generation engine} using Jinja templates that converts page metadata into pytest-compatible regression scripts with Page Object Model classes for every discovered page.
  \item \textbf{Designed and dockerized 3 microservices} -- Recorder (Playwright codegen), MCP Service (AI agent + test generation), and Execution Service (isolated runner) -- saving 100+ team-hours weekly and cutting QA costs by \$230K/year.
\end{itemize}

\project{AI-Powered IVR Automation -- Cotiviti}{Java, Python, LangGraph, AWS Bedrock, Transcribe, DynamoDB, Lambda, SQS, KMS, Twilio}
\\[2pt]
{\small\textit{Cotiviti's Medicare IVR verification ran on legacy Jabber VMs, requiring a human to manually review and update navigation paths every morning. The team migrated to a fully serverless, horizontally scalable AWS architecture and introduced an AI agent that autonomously discovers the correct IVR path daily, eliminating the manual review step entirely.}}
\begin{itemize}
  \item \textbf{Designed an AI pathfinding workflow with LangGraph and AWS Bedrock} that navigates Medicare's IVR daily -- recording calls via Twilio, transcribing with AWS Transcribe, and writing the correct DTMF path to DynamoDB for 200,000+ daily production calls.
  \item \textbf{Built a mock Medicare IVR simulator} in Java as a regression harness, validating AI agent accuracy against simulated decision trees before production deployment.
  \item \textbf{Configured the AWS CI/CD pipeline} (CodePipeline) with KMS-encrypted PII handling across all environments.
  \item \textbf{Part of a cross-functional team} that saved 730+ engineer-hours annually and cut infrastructure costs by $\sim$60\% through serverless auto-scaling.
\end{itemize}

\divider

\employer{University at Buffalo}{AI Research Assistant}{Jan 2024 -- May 2024}

\project{Energy-Efficient LLM Inference and Carbon-Aware Optimization}{Python, PyTorch, TensorFlow, Hugging Face, NumPy, Pandas}
\begin{itemize}
  \item \textbf{Benchmarked parameter-efficient fine-tuning (PEFT) techniques} -- LoRA, knowledge distillation, and post-training quantization (4-bit/8-bit) -- on GPT-2, measuring GPU energy consumption and carbon emissions across task configurations.
  \item \textbf{Achieved 19.8\% CO2 reduction} with only 6\% perplexity increase using 8-bit quantization, demonstrating significant energy savings with minimal quality degradation.
  \item \textbf{Demonstrated 45.2\% emissions reduction} by combining distillation with quantization, mapping the accuracy-efficiency trade-off curve for carbon-aware deployment.
\end{itemize}

\divider

\employer{Flable AI}{Machine Learning Engineer}{Mar 2023 -- Aug 2023}

\project{Flable Digital Assistant}{Python, LangChain, OpenAI, PostgreSQL, FastAPI, Docker, Jenkins, GitLab}
\begin{itemize}
  \item \textbf{Built a LangChain conversational AI with OpenAI} that classifies user intent via transformer embeddings, maps queries to PostgreSQL data categories, and generates natural-language responses grounded in real results.
  \item \textbf{Developed an on-the-fly visualization engine} that dynamically queries PostgreSQL, renders charts, and delivers them inline via Telegram -- giving non-technical users instant access to analytics.
  \item \textbf{Deployed the full stack} (FastAPI backend + Telegram bot) using Docker with GitLab CI/CD and Jenkins pipelines, reducing client's weekly analysis time by 60\%.
\end{itemize}

\end{rSection}

%==============================================================================
% OPEN SOURCE
%==============================================================================
\begin{rSection}{Open Source}

\textbf{langgraph-checkpoint-cosmos} \enspace\textcolor{techgray}{$\mid$}\enspace \href{https://github.com/LangModule/checkpoint-cosmos}{\faGithub\ github.com/LangModule/checkpoint-cosmos}
\begin{itemize}
  \item Published a LangGraph checkpoint saver for Azure Cosmos DB with sync/async support, tip-document optimization, transactional consistency, and DefaultAzureCredential keyless authentication.
\end{itemize}

\end{rSection}

%==============================================================================
% EDUCATION
%==============================================================================
\begin{rSection}{Education}

\textbf{University at Buffalo, The State University of New York} \hfill Buffalo, New York \\
Master of Science, Computer Science, CGPA: 3.7/4 \hfill Aug 2023 -- Dec 2024 \\
\textit{Coursework: Data Intensive Computing, Computer Vision, Machine Learning, Deep Learning}

\end{rSection}

\end{document}
